---
title: "OneDayExample"
author: "Pavel Fiser"
date: "April 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Co-jump estimation - one day example
Example code which replicates JWTSRV (Barunik and Vacha, 2015 QF) and JWTSCV (Barunik and Vacha, 2018 JFM) methods and is applied in Barunik and Fiser 2019. The main advantage of the wavelet-based estimation is the ability of wavelets to precisely separate the continuous price process into
continuous and discontinuous parts even when data are covered with noise. For more details about the method see (Barunik and Vacha, 2018 JFM).

The code has been developed in R version 3.5.0.
```{r functions, echo = FALSE}
################################################################################
#                             Quadratic variation                              # 
################################################################################
# Calculation of quadratic variation and covariation  
QVCalculation <- function(returns1, returns2){
  QV <- sum(returns1 * returns2)
  return(QV)
}

################################################################################
#                      Integrated covariance estimation                        # 
################################################################################
ICestimation <- function(return1, 
                         return2, 
                         Nobservations5Min,
                         nameReturn1 = "Return1",
                         nameReturn2 = "Return2",
                         fixedG = NA_real_){
  # Zhang(2011) G parameter - tuned based on number of intraday observations
  # Calculated as floor of "Number of intraday observations in examined frequency" (1min in our example) 
  # deviede by ("number of intraday observations in 5 minute frequency"/2.3)
  Nobservations <- length(return1)
  
  if(is.na(fixedG)) {
    Nobservations5Min <- Nobservations5Min
    G <- floor(Nobservations/(Nobservations5Min / 2.3)) 
  } else {
    G <- fixedG
  }
  
  # data reshape - for ICG and IC calculation 
  GNobservations <- floor(Nobservations/G)
  split <- Nobservations - G*GNobservations + 1
  
  dataReturn1 <- matrix(0, nrow = GNobservations, ncol = G)
  dataReturn2 <- matrix(0, nrow = GNobservations, ncol = G)
  
  for (start in 1:split) {
    dataReturn1[1:GNobservations,start] <- rowSums( matrix(return1[start:((start-1)+G*floor((Nobservations - start + 1)/G))],ncol=G, byrow = T) )
    dataReturn2[1:GNobservations,start] <- rowSums( matrix(return2[start:((start-1)+G*floor((Nobservations - start + 1)/G))],ncol=G, byrow = T) )
  }
  
  for (start in (split+1):G) {
    dataReturn1[1:(GNobservations-1),start] <- rowSums( matrix(return1[start:((start-1)+G*floor((Nobservations - start + 1)/G))],ncol=G, byrow = T) )
    dataReturn2[1:(GNobservations-1),start] <- rowSums( matrix(return2[start:((start-1)+G*floor((Nobservations - start + 1)/G))],ncol=G, byrow = T) )
  }
  
  # QV for every time point
  dataReturn1Return1 <- dataReturn1 *dataReturn1 
  dataReturn2Return2 <- dataReturn2 *dataReturn2 
  dataReturn1Return2 <- dataReturn1 *dataReturn2 
  
  # IC(G) 
  ICG.Return1Return1    <- colSums(dataReturn1Return1)
  ICG.Return1Return1avg <- mean(ICG.Return1Return1)
  
  ICG.Return2Return2    <- colSums(dataReturn2Return2)
  ICG.Return2Return2avg <- mean(ICG.Return2Return2)
  
  ICG.Return1Return2    <- colSums(dataReturn1Return2)
  ICG.Return1Return2avg <- mean(ICG.Return1Return2)
  
  # IC (WRC)
  ICWRC.Return1Return1 <- QVCalculation(return1,return1) 
  ICWRC.Return2Return2 <- QVCalculation(return2,return2) 
  ICWRC.Return1Return2 <- QVCalculation(return1,return2)  
  
  #constants
  nbar_N <- (( GNobservations*split + ( (GNobservations-1)*(G-split) ) )/G)/Nobservations
  const_ICG <- 1/(1-nbar_N)
  const_ICWRC <- const_ICG*nbar_N
  
  # IC calculation
  IC.Return1Return1 <- const_ICG * ICG.Return1Return1avg - const_ICWRC * ICWRC.Return1Return1
  IC.Return2Return2 <- const_ICG * ICG.Return2Return2avg - const_ICWRC * ICWRC.Return2Return2
  IC.Return1Return2 <- const_ICG * ICG.Return1Return2avg - const_ICWRC * ICWRC.Return1Return2
  
  # correlation culculation
  rho.Return1Return2 <- IC.Return1Return2/(sqrt(IC.Return1Return1)*sqrt(IC.Return2Return2))
  
  # results compilation
  ICmat.Return1Return2 <- data.frame(IC.Return1Return2,
                                     IC.Return1Return1,
                                     IC.Return2Return2, 
                                     rho.Return1Return2)
  
  names(ICmat.Return1Return2) <- c(paste0("IC.",nameReturn1,nameReturn2), 
                                   paste0("IC.",nameReturn1,nameReturn1),
                                   paste0("IC.",nameReturn2,nameReturn2), 
                                   paste0("rho.",nameReturn1,nameReturn2))
  
  return(ICmat.Return1Return2)
}

################################################################################
#                       Jump estimation - 1 minute data                        # 
################################################################################
# Function for jump identification - use "modwt" from "wavelets" package for calculation of wavelet coefficients
# carefull about the boundary option - "reflection" returns twice as many coefficients
# "periodic" is better for matching the time stamp of the jump
JumpIdentification <- function(return, filter = "d4", boundary = "periodic"){
  
  # calculation of first wavelet coefficients
  modwt <- align(modwt(as.numeric(return),filter = filter, n.levels = 1, boundary = boundary))@W[[1]] 
  nonzero_modwt <- modwt[!modwt == 0]                                                                     
  
  # Donoho & Johnstone (1994) threshold
  epsilon <- sqrt(2)*median(abs(nonzero_modwt))*sqrt(2*log(length(nonzero_modwt)))/0.6745
  
  # jump identification
  Jump <- abs(modwt) > epsilon
  
  # Calculating returns value without jumps, if jump occured the return is replaced with intraday variation 
  returnNoJ <- return * (Jump == FALSE) + Jump * var(return) * (return > 0) - Jump * var(return) *(return < 0)
  
  # Jump is calculated as returns - returns withou jumps
  JumpSize <- return - returnNoJ 
  
  return(data.frame("Jump" = Jump,
                    "dlCloseNoJ" = returnNoJ,
                    "JumpSize" = JumpSize))
  
}

################################################################################
#                                 Bootstrap                                    # 
################################################################################
# function for simulation 1 second data
sim_ret_intraday <- function(IC_mtx,N,day){
  error_TS1 <- rnorm(N,mean = 0, sd = 1)
  error_TS2 <- rnorm(N,mean = 0, sd = 1) 
  rho_TS1_TS2 <- IC_mtx[,4]
  ret_sim_TS1 <- sqrt(1/N*IC_mtx[,2][day])*error_TS1 
  ret_sim_TS2 <- sqrt(1/N*IC_mtx[,3][day])*(IC_mtx[,4][day]*error_TS1 + sqrt(1-IC_mtx[,4][day]^2)*error_TS2)
  df <- cbind.data.frame(ret_sim_TS1,ret_sim_TS2)
  df
}

# bootstrap function 
bootstrapIntraday <- function(ICJWCmatrix,Nobservations.boot,fixedG){
  # simulate 1 second data
  ret_1_2_mtx <- sim_ret_intraday(ICJWCmatrix,Nobservations.boot,1)             
  
  # reshape data into 5 minute intervals - 1 row contains 5 minute data i.e. 300s 
  ret_sim_R1 <- matrix(ret_1_2_mtx[,1],ncol = 5*60, byrow = T)
  ret_sim_R2 <- matrix(ret_1_2_mtx[,2],ncol = 5*60, byrow = T)
  
  # calculate intraday realized variance / covariance
  RV_boot1 <- sum( rowSums(ret_sim_R1)^2 )
  RV_boot2 <- sum( rowSums(ret_sim_R2)^2 )
  RV_boot12 <- sum( rowSums(ret_sim_R1)*rowSums(ret_sim_R2) )
  
  # estimate IC 
  ICJWCSim <- ICestimation(ret_1_2_mtx[,1],ret_1_2_mtx[,2], Nobservations5Min = NA, fixedG = fixedG)
  
  # calculate z value - (RV - IC)/RV
  Z_12 <- (RV_boot12 - ICJWCSim$IC.Return1Return2)/(RV_boot12) 
  Z_11 <- (RV_boot1  - ICJWCSim$IC.Return1Return1)/(RV_boot1)
  Z_22 <- (RV_boot2  - ICJWCSim$IC.Return2Return2)/(RV_boot2)
  
  return(data.frame(Z.12 = Z_12,
                    Z.11 = Z_11,
                    Z.22 = Z_22))
}

################################################################################
#                                  Results                                     # 
################################################################################
# Function to calculate final QV, IC, CJ for intraday data
hypothesisAnalysis <- function(Zstatus, QVmat, ICmat, CJmat){
  finalresults <- data.frame("QV"          = NA,
                             "CJvariation" = NA,
                             "CJ"          = NA,
                             "Jidio"       = NA, 
                             "ICJWCfinal"  = NA)
  
  for(i in 1:length(Zstatus)){
    QV          <- QVmat[i]
    
    if(Zstatus[i]){
      CJvariation <- QV - ICmat[i]
      CJ          <- CJmat[i]
      Jidio       <- CJvariation - CJmat[i]
      ICJWCfinal  <- ICmat[i]
    } else {
      CJvariation <- 0
      CJ          <- 0
      Jidio       <- 0
      ICJWCfinal  <- QVmat[i]
    }
    
    finalresults <- rbind(finalresults, list("QV"          = as.numeric(QV) ,
                                             "CJvariation" = as.numeric(CJvariation),
                                             "CJ"          = CJ,
                                             "Jidio"       = as.numeric(Jidio),
                                             "ICJWCfinal"  = as.numeric(ICJWCfinal))
    )
  }
  
  finalresults <- finalresults[-1,] 
  return(finalresults)
}

``` 

### Required packages and functions
Load required packages
```{r packages, message = FALSE, warning = FALSE}
library(wavelets)
library(dplyr)
```

Source functions used in the analyses
``` {r sourcefunctions, eval = FALSE}
source('.OneDayExample/OneDayExampleFunctions.R')
```

### Example data used for the analysis
One trading day data of two time series (BN, BX) - Log returns (dlClose) with one minute and five minute frequency - are used for the analysis. 

```{r DataLoad}
BNday_5min <- readRDS("BNdayExample_5min.rds")
BXday_5min <- readRDS("BXdayExample_5min.rds")

BNday_1min <- readRDS("BNdayExample_1min.rds")
BXday_1min <- readRDS("BXdayExample_1min.rds")
```

## Realized Quadratic variation / covariation
Realized quadratic variation and covariation is estimated using five minute frequency data.
``` {r QV}
QV_BNBN <- QVCalculation(BNday_5min$dlClose, BNday_5min$dlClose)
QV_BXBX <- QVCalculation(BXday_5min$dlClose, BXday_5min$dlClose)
QV_BNBX <- QVCalculation(BNday_5min$dlClose, BXday_5min$dlClose)

QVmat.BNBX <- data.frame(QV_BNBX,
                         QV_BNBN,
                         QV_BXBX)

QVmat.BNBX
```

## Integrated covariance two-scale realized covariance - with jumps (IC TSCV)
Observed data with both microstructure noise and jumps are used for estimation of Integraded covariance - two scaled realized covariance. Ic TSCV matrix is than used for calcualtion of corresponding correlation. 
```{r ICTSCV}
# Extract returns from the data 
retBN <- BNday_1min$dlClose
retBX <- BXday_1min$dlClose

# IC TSCV estimation
ICTSCVmat.BNBX <- ICestimation(retBN, 
                               retBX, 
                               nrow(BNday_5min),
                               "BN",
                               "BX")

ICTSCVmat.BNBX
```


## Jump identification and estimation 
The position of jumps is identified and subsequently jumps are estimated using one minute data. Subsequently "jump estimates" are substracted from the "observed returns" and "jump adjusted returns" are obtained.

```{r Jumps, warning = FALSE}
BNday_1min <- cbind(BNday_1min, 
                    JumpIdentification(BNday_1min$dlClose))

BXday_1min <- cbind(BXday_1min, 
                    JumpIdentification(BXday_1min$dlClose) )

BNday_1min %>% filter(Hour == 14 & Min %in% c(30:35))
```

## Co-jump identification 
Once we have jumps identified and estimated we proceed with co-jump identification. 
```{r cojump}
CJ.BNBX <- BNday_1min$JumpSize * BXday_1min$JumpSize 
CJintraday <- sum(CJ.BNBX)
CJintraday
```


## Integrated covariance jump wavelet covariance - without jumps (IC JWC)
Above obtained "jump adjusted returns" are used for estimation of Integraded covariance - Jump wavelet covariance.
```{r ICJWC}
retBNNoJ <- BNday_1min$dlCloseNoJ
retBXNoJ <- BXday_1min$dlCloseNoJ

# IC JWC estimation
ICJWCmat.BNBX <- ICestimation(retBNNoJ,
                              retBXNoJ, 
                              nrow(BNday_5min),
                              "BN",
                              "BX")
ICJWCmat.BNBX
```

## Bootstrap 
Estimated IC JWC is used for bootstap to obtain Z values estimates. 

```{r bootstrap}
# We are generating 1 second data in the bootstrap - Nobservations.boot 
Nobservations <- nrow(BNday_1min)
Nobservations.boot <- Nobservations * 60

# Fixed G is used in this case, see Zhang(2011) for more details
fixedG <- 75 

# number of bootstrap loops
b <- 100

# set seed for replication purposes 
seed <- 12
set.seed(seed)

# Bootstrap realizations - Z* values
Zvalues <- data.frame("Z.12" = NA, "Z.11" = NA, "Z.22" = NA)
for(B in 1:b){
   Zvalues <- rbind(Zvalues,
                    bootstrapIntraday(ICJWCmat.BNBX,Nobservations.boot,fixedG)[1:3])
}
Zvalues <- Zvalues[-1,]
colnames(Zvalues) <- c("Z.BNBX", "Z.BNBN", "Z.BXBX")  
head(Zvalues)
```


## Hypothesis testing - Co-jump estimation
With Z values estimated we calculate Z statistic and test the null hypothesis of no presence of jumps and co-jumps in the observed returns.
```{r hypothesis}
# values for one-sided and two-sided t-test
ci <- 2.5767
ci2 <- 1.968

# Combining co-jumps data of one pair together 
CJmat.BNBX <- c(CJintraday,0,0)

# Calculation of Z value from calculated data
Zvalue.BNBX <- (QVmat.BNBX - ICJWCmat.BNBX[1:3])/QVmat.BNBX

# Calculation of Z bootstrap statistic
Zstatistic.BNBX <- (Zvalue.BNBX - colMeans(Zvalues))/sqrt(diag(var(Zvalues)))

# Hausman test for hypothesis testing
Zstatus <- c(Zstatistic.BNBX[1] > ci2, Zstatistic.BNBX[2:3] > ci) 

# Identification of significant co-jump variation
results <- hypothesisAnalysis(Zstatus,QVmat.BNBX,ICJWCmat.BNBX[1:3],CJmat.BNBX)
rownames(results) <- c("BNBX","BNBN", "BXBX")
results
```


## Correlation difference analysis
```{r correlation}
# correlation difference
corrTrue.BNBX <- ICTSCVmat.BNBX$rho.BNBX
corrContinuous.BNBX <- results["BNBX",]$ICJWCfinal/(sqrt(results["BNBN",]$ICJWCfinal) * sqrt(results["BXBX",]$ICJWCfinal))
corrDifference.BNBX <- corrTrue.BNBX - corrContinuous.BNBX

correlation <- data.frame("True"       = corrTrue.BNBX,
                          "Continuous" = corrContinuous.BNBX,
                          "Difference" = corrDifference.BNBX)

correlation
```